Sequence Specific Modeling of \emph{E.~coli} Cell-Free Protein Synthesis

### 2017-05-05 Paper_v1.tex
Small changes

\begin{figure}[t!]
\includegraphics[width=1.00\textwidth]{./figs/Fig-5-FluxDistribition-Optimal.pdf}
\caption{Flux profile for glycolysis, pentose phosphate pathway, Entner-Doudoroff pathway, TCA cycle, and oxidative phosphorylation, for three different cases: (A) amino acid uptake and synthesis, (B) amino acid uptake without synthesis, and (C) amino acid synthesis without uptake. Mean flux across the ensemble, normalized to glucose uptake flux. Thick arrows indicate flux to or from amino acids.}
\label{fig:flux}
\end{figure}

@@

\begin{figure}[t!]
\includegraphics[width=0.7\textwidth]{./figs/Fig-4-OxyPhox-versus-Carbon-Yield.pdf}
\caption{The deGFP carbon yield versus oxidative phosphorylation flux, across an ensemble of 1000 flux balance solutions, for amino acid uptake and synthesis (black), amino acid uptake without synthesis (dark grey), and amino acid synthesis without uptake (light gray).}
\label{fig:oxphos_yield}
\end{figure}

@@

\begin{figure}[t!]
\includegraphics[width=1.0\textwidth]{./figs/Fig-7-FluxDistribution-Analysis.pdf}
\caption{The norm effect of pairwise knockouts of subgroups in the cell-free network.
(A) CAT productivity norm compared to no knockouts in the experimentally constrained case.
(B) Flux distribution norm compared to no knockouts in the experimentally constrained case.}
\label{fig:norm}
\end{figure}

>>>>

\begin{figure}[t!]
\includegraphics[width=1.00\textwidth]{./figs/Fig-5-FluxDistribition-Optimal.pdf}
\caption{Flux profile for glycolysis, pentose phosphate pathway, Entner-Doudoroff pathway,
TCA cycle, and oxidative phosphorylation, for: (A) amino acid supplementation and \textit{de~novo} synthesis,
(B) amino acid supplementation without \textit{de~novo} synthesis, and
(C) \textit{de~novo} amino acid synthesis without supplementation.
Mean flux across the ensemble, normalized to glucose uptake flux. Thick arrows indicate flux to or from amino acids.}
\label{fig:flux}
\end{figure}

@@

\begin{figure}[t!]
\includegraphics[width=0.7\textwidth]{./figs/Fig-4-OxyPhox-versus-Carbon-Yield.pdf}
\caption{The CAT carbon yield versus oxidative phosphorylation flux, across an ensemble of 1000 flux balance solutions,
for amino acid supplementation and \textit{de~novo} synthesis (black),
amino acid supplementation without \textit{de~novo} synthesis (dark grey),
and \textit{de~novo} amino acid synthesis without supplementation (light gray).}
\label{fig:oxphos_yield}
\end{figure}

@@

\begin{figure}[t!]
\includegraphics[width=1.0\textwidth]{./figs/Fig-7-FluxDistribution-Analysis.pdf}
\caption{Pairwise knockouts of reaction subgroup in the cell-free network.
(A) Difference in the CAT productivity in the presence of reaction knockouts compared to no knockouts for the experimentally constrained case.
(B) Difference in the optimal flux distribution in the presence of reaction knockouts compared to no knockouts in the experimentally constrained case.
The difference between perturbed and wild-type productivity and flux distributions was quantified by the $l^{2}$ norm, and then normalized so the maximum change was 1.0.
Red boxes indicate potential alternative optimal flux distributions.}
\label{fig:norm}
\end{figure}
